---
title: "Multiple Boxplots in One graph in R"
output: html_notebook
---
#### Md Irfan Hossain
#### Code courtesy: statisticsglobe.com
# Creation of Example Data
```{r}
set.seed(123456)
data<-data.frame(A = rnorm(1000), B = runif(1000), C=rpois(1000,3))
head(data)
```
# Example 1: Drawing multiple boxplots using Base R
```{r}
boxplot(data)
```
# Example 2: Drawing multiple boxplots using ggplot2 package
## Installing reshape2 pacakge
```{r}
install.packages("reshape2")
library("reshape2")
```

## Converting data to long format
```{r}
data_long<-melt(data)
head(data_long)
```
## Installing ggplot2 pacakge
```{r}
install.packages("ggplot2")
library("ggplot2")
```
## multiple boxplots using ggplot
```{r}
ggplot(data_long, aes(x=variable, y=value))+geom_boxplot()
```
# Example 3: Drawing multiple boxplots using lattice
## Installing lattice pacakge
```{r}
install.packages("lattice")
library("lattice")
```
## multiple boxplots using bwplot
```{r}
bwplot(value ~ variable, data_long)
```
# Example 4: Drawing multiple boxplots for groups in ggplot
## Calling the in-built iris dataset & reshaping it
```{r}
data(iris)
iris_long<-melt(iris, id ="Species")
head(iris_long)
```
## Multiple boxplots using ggplot
```{r}
ggplot(iris_long, aes(x=variable, y=value, color=Species))+geom_boxplot()
```